\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.35in}
\setlength{\footskip}{4.1pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

\begin{center}
    \textbf{\huge \scshape Wenfeng Liang} \\ \vspace{1pt}
    \small Hangzhou, China $|$
    Founder \& CEO, DeepSeek $|$
    Co-founder, High-Flyer Quant \\
    \small \href{https://www.deepseek.com}{deepseek.com} $|$
    \href{https://github.com/deepseek-ai}{github.com/deepseek-ai}
\end{center}

\section{Summary}
\small{AI founder and quantitative systems builder focused on frontier LLMs, reasoning systems, and efficient training infrastructure. Founded DeepSeek in 2023; previously co-founded High-Flyer Quant, applying machine learning, large-scale data systems, and automated research pipelines to quantitative investment.}

\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {DeepSeek}{Hangzhou, China}
    {Founder and Chief Executive Officer}{2023 -- Present}
    \resumeItemListStart
      \resumeItem{Set technical direction for open-weight LLMs, reasoning models, and cost-efficient training systems.}
      \resumeItem{Built teams across architecture, pretraining, reinforcement learning, evaluation, systems, and inference optimization.}
      \resumeItem{Led public model releases emphasizing practical deployment, open access, and transparent technical reporting.}
    \resumeItemListEnd

  \resumeSubheading
    {High-Flyer Quant}{Hangzhou, China}
    {Co-founder and Quantitative Research Leader}{2015 -- Present}
    \resumeItemListStart
      \resumeItem{Co-founded an AI-driven quantitative investment firm using statistical learning and large-scale feature engineering for systematic trading.}
      \resumeItem{Directed investment in compute infrastructure, automated research pipelines, and production model deployment.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Selected Technical Leadership}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Open Large Language Model Development} $|$ \emph{LLM pretraining, alignment, inference}}{2023 -- Present}
    \resumeItemListStart
      \resumeItem{Led open model releases designed for broad developer access, independent evaluation, and efficient deployment.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Reasoning Model Systems} $|$ \emph{reinforcement learning, evaluation, scalable training}}{2024 -- Present}
    \resumeItemListStart
      \resumeItem{Coordinated data generation, reward design, distributed training, evaluation, and inference-time behavior.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{AI Quant Research Infrastructure} $|$ \emph{ML systems, data platforms, distributed compute}}{2015 -- 2023}
    \resumeItemListStart
      \resumeItem{Built research infrastructure for data ingestion, model training, experiment tracking, backtesting, and production deployment.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Selected Publications and Technical Reports}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{DeepSeek-V3 Technical Report} $|$ \emph{DeepSeek-AI technical report}}{2024}
    \resumeItemListStart
      \resumeItem{Co-authored technical report describing the DeepSeek-V3 model family, including model architecture, training pipeline, efficiency choices, and evaluation results.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Native Sparse Attention} $|$ \emph{efficient long-context attention}}{2025}
    \resumeItemListStart
      \resumeItem{Co-authored study on sparse attention mechanisms for improving efficiency when processing long-context model inputs.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Insights into DeepSeek-V3} $|$ \emph{scaling and hardware-software co-design}}{2025}
    \resumeItemListStart
      \resumeItem{Co-authored technical analysis on scaling challenges, memory efficiency, inter-chip communication, and hardware-aware AI infrastructure design.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Zhejiang University}{Hangzhou, China}
    {M.S. in Information and Communication Engineering}{Completed 2010}
  \resumeSubheading
    {Zhejiang University}{Hangzhou, China}
    {B.S. in Electronics and Communication Engineering}{Completed 2007}
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Research Areas}{: large language models, reasoning models, reinforcement learning, quantitative modeling, statistical learning, model evaluation} \\
    \textbf{Systems}{: distributed training, GPU clusters, data pipelines, model serving, experiment infrastructure, high-throughput inference} \\
    \textbf{Leadership}{: research strategy, open-source model release, AI lab building, technical recruiting, cross-functional engineering management}
  }}
\end{itemize}

\end{document}
